Learning can mediate the evolution of\\ (cheap and costly) signals of quality

### 2020-10-27 Presentations/GenesAsEnviron.Rmd
cpp code: a bug fixed in the records of interactions in each generations. New simulations started (par2Json):starting  values for 3d reaction norms had the opposite sign. Moving forward in the presentation for AGA

```{r,echo=FALSE,fig.align="center",out.width='80%'}
knitr::include_graphics("../Images/harm.jpg")
```

@@

### When are signals honest?

* Impossible to fake
* Individuals have common interests
* Handicap principle (signal´s cost is proportional to quality)

### Individual recognition

```{r,echo=FALSE,fig.align='center',out.height='70%'}
knitr::include_graphics("../Images//indRecog.png")

```
[@tibbetts_Individual_2007]

### BS or IR?

```{r,echo=FALSE,fig.align='center',out.height='75%'}
knitr::include_graphics("../Images//IRvsBS.png")

```
[@sheehan_There_2016]

@@

```{r,echo=FALSE,fig.align='center',out.width='90%'}
knitr::include_graphics("../Images//pavlov.jpg")
```

>>>>

@@

### The handicap principle

```{r,echo=FALSE,fig.align='center',out.height='35%',fig.show='hold'}
knitr::include_graphics("../Images/Amotz_Zahavi_profile.jpg")
knitr::include_graphics("../Images/sexualSelection.jpg")
knitr::include_graphics("../Images/Grafen.jpg")
```

```{r,echo=FALSE,fig.align='center',out.height='35%'}

badQualRang<-seq(0,1,length=1000)
alpha<-0
beta<-6
costFunc<-function(beta,alpha,x) {d<-1/(1+exp(-alpha-beta*x))}
par(plt=posPlot())
betRang<-c(5)
matplot(y=sapply(betRang,FUN = costFunc,alpha=alpha,x=badQualRang),x=badQualRang,
        type="l",cex.lab=1.5, cex.axis=2,lwd=3,lty=1,las=1,
     col=c(2,3),ylim=c(0.5,1.1),xaxt="s",yaxt="s",ylab="",xlab="") #,col=i
# lines(badgeFunc(qualRange,3,-60,1.05)~qualRange,cex.lab=1.5,cex.axis=2,lwd=3,
#       col="blue")
# legend("bottomright",legend = betRang,title = expression(beta),col=1:3,
       # lty=1)
mtext(side=1,text="Quality",line=3.5,cex=3)
mtext(side=2,text="Survival",line=3.5,cex=3)

```
[@zahavi_Mate_1975;@grafen_Biological_1990]

## The handicap principle

### Badges of status

@@

```{r,echo=FALSE,fig.align='center',out.width='70%'}
knitr::include_graphics("../Images//pavlov.jpg")
```

### 2020-10-27 Presentations/GenesAsEnviron.tex
cpp code: a bug fixed in the records of interactions in each generations. New simulations started (par2Json):starting  values for 3d reaction norms had the opposite sign. Moving forward in the presentation for AGA

\title{Learning can mediate the evolution of\\
(cheap and costly) signals of quality}
\author{Andrés Quiñones PhD.}
\date{Genes as environment - AGA2020 virtual symposium\\
October 21, 2020}

@@

\begin{center}\includegraphics[width=0.8\linewidth]{../Images/harm} \end{center}

@@

\begin{frame}{What about signals?}
\protect\hypertarget{what-about-signals-1}{}

\begin{block}{When are signals honest?}

\begin{itemize}
\tightlist
\item
  Impossible to fake
\item
  Individuals have common interests
\item
  Handicap principle (signal´s cost is proportional to quality)
\end{itemize}

@@

\begin{frame}{What about signals?}
\protect\hypertarget{what-about-signals-2}{}

\begin{block}{Individual recognition}

\begin{center}\includegraphics[height=0.7\textheight]{../Images//indRecog} \end{center}

(Tibbetts and Dale 2007)

@@

\begin{frame}{What about signals?}
\protect\hypertarget{what-about-signals-3}{}

\begin{block}{BS or IR?}

\begin{center}\includegraphics[height=0.75\textheight]{../Images//IRvsBS} \end{center}

(Sheehan and Bergman 2016)

\begin{frame}{What about signals?}
\protect\hypertarget{what-about-signals-4}{}

@@

\begin{center}\includegraphics[width=0.9\linewidth]{../Images//pavlov} \end{center}

@@

@@

\begin{center}\includegraphics[width=0.5\linewidth]{GenesAsEnviron_files/figure-beamer/unnamed-chunk-12-1} \end{center}

@@

\caption{alpha - beta -Badge}\label{fig:unnamed-chunk-17}
\end{figure}

@@

\caption{alpha - beta -Badge}\label{fig:unnamed-chunk-23}
\end{figure}

@@

\leavevmode\hypertarget{ref-sheehan_There_2016}{}%
Sheehan, Michael J., and Thore J. Bergman. 2016. ``Is There an
Evolutionary Trade-Off Between Quality Signaling and Social
Recognition?'' \emph{Behav Ecol} 27 (1): 2--13.
\url{https://doi.org/10.1093/beheco/arv109}.

\leavevmode\hypertarget{ref-tibbetts_Individual_2007}{}%
Tibbetts, Elizabeth A., and James Dale. 2007. ``Individual Recognition:
It Is Good to Be Different.'' \emph{Trends in Ecology \& Evolution} 22
(10): 529--37. \url{https://doi.org/10.1016/j.tree.2007.09.001}.

>>>>

\title{Learning can mediate the evolution of\\
(cheap and costly) signals of quality}
\author{Andrés Quiñones PhD.}
\date{Genes as environment - AGA2020 virtual symposium\\
October 26, 2020}

@@

@@

\begin{block}{The handicap principle}

\begin{center}\includegraphics[height=0.35\textheight]{../Images/Amotz_Zahavi_profile} \includegraphics[height=0.35\textheight]{../Images/sexualSelection} \includegraphics[height=0.35\textheight]{../Images/Grafen} \end{center}

\begin{center}\includegraphics[height=0.35\textheight]{GenesAsEnviron_files/figure-beamer/unnamed-chunk-4-1} \end{center}

(Zahavi 1975; Grafen 1990)

@@

\begin{frame}{The handicap principle}
\protect\hypertarget{the-handicap-principle-1}{}

\begin{block}{Badges of status}

@@

@@

\begin{center}\includegraphics[width=0.7\linewidth]{../Images//pavlov} \end{center}

@@

\begin{center}\includegraphics[width=0.5\linewidth]{GenesAsEnviron_files/figure-beamer/unnamed-chunk-10-1} \end{center}

@@

@@

\caption{alpha - beta -Badge}\label{fig:unnamed-chunk-16}
\end{figure}

@@

\caption{alpha - beta -Badge}\label{fig:unnamed-chunk-22}
\end{figure}

@@

\leavevmode\hypertarget{ref-grafen_Biological_1990}{}%
Grafen, Alan. 1990. ``Biological Signals as Handicaps.'' \emph{Journal
of Theoretical Biology} 144 (4): 517--46.
\url{https://doi.org/10.1016/S0022-5193(05)80088-8}.

\leavevmode\hypertarget{ref-zahavi_Mate_1975}{}%
Zahavi, Amotz. 1975. ``Mate Selection-A Selection for a Handicap.''
\emph{Journal of Theoretical Biology} 53 (1): 205--14.
\url{https://doi.org/10.1016/0022-5193(75)90111-3}.
